### 2022-11-24 files/Overview.tex
Overview v2.2

\subsubsection{Finite element method}
This chapter is preperation for the final chapter in this dissertation. The finite element method is applied to the models of this dissertation. Specifically, it is applied to the Cantilever model problem of the three-dimensional and two-dimensional elastic bosies, as well as the cantilever plate model. The cantilever Timoshenko beam model is excluded since chapter 4 provides an exact method to calculate the eigenvalues and eigenfunctions. Each of the models are assumed to have a rectangular cross-section and is made of the same isotropic material.

to a cantilever version of each of the models in this dissertation. The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model. The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4 (\cite{VV02}). The model is assumed to have a rectangular cross-section and is in a cantilever configuration. The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given. In this numerical formula, the model problem is a system of linear equations. This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\

@@

In this chapter, the validity of the models in this dissertation is investigated using numerical results. Specifically the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate is investigated. In this case, the term validity refers to how well the model compares to a more realistic model. All models are assumed to have a rectangular cross-section, are in a cantilever configuration and are made of the same isotropic material. This first section, is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of the Timoshenko beam model. The authors compare the Timoshenko beam model to a more realistic two-dimensional beam model. The comparison is made with the eigenvalues and eigenfunctions. From modal analysis it is known that the solution of the models are linear combinations of the eigenvalues and eigenfunctions. The two-dimensional model also have eigenvalues that do not have a corresponding eigenvalue in the Timoshenko beam model. The authors call all matching eigenvalues beam-type eigenvalues. The authors show that the Timoshenko beam model compare well to the two-dimensional model for long and short beams. The results of the article are verified and extra results are also calculated for the rest of this chapter. In this section, the aricle \cite{LVV09} is extended to verify the validity of the two-dimensional elastic model. The two-dimensional elastic model is compared to a more realistic three-dimensional model. The two dimensional model serves as a intermediate step between the Timoshenko beam model and the three-dimensional model. The same approach of \cite{LVV09} is used to compare the two models. The result show that the two-dimensional model compare very well to the three-dimensional model, especially for beam problems. The last section takes the idea of \cite{LVV09} and extends it to the Reissner-Mindlin plate model. The Reissner-Mindlin plate model is compared to a more realistic three-dimensional plate model.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsubsection{Finite element method}
This chapter is preperation for the final chapter in this dissertation. The finite element method is applied to the models of this dissertation. Specifically, it is applied to the Cantilever model problem of the three-dimensional and two-dimensional elastic bosies, as well as the cantilever plate model. The cantilever Timoshenko beam model is excluded since chapter 4 provides an exact method to calculate the eigenvalues and eigenfunctions. Each of the models are assumed to have a rectangular cross-section and is made of the same isotropic material. For each model, a reference configuration is defined. The Galerkin approximation can then be derived and using the Finite Element Method, a system of oridinary differential equations can be obatined. At this point is it easy to derive a eigenvalue problem for each of the models. This eigenvalue problem can be solved using numerical methods.

@@

In this chapter, the validity of the models in this dissertation is investigated using numerical results. Specifically the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate is investigated. In this case, the term validity refers to how well the model compares to a more realistic model. All models are assumed to have a rectangular cross-section, are in a cantilever configuration and are made of the same isotropic material. The first section, is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of the Timoshenko beam model. The authors compare the Timoshenko beam model to a more realistic two-dimensional beam model. The comparison is made with the eigenvalues and eigenfunctions. From modal analysis it is known that the solution of the models are linear combinations of the eigenvalues and eigenfunctions. The two-dimensional model also have eigenvalues that do not have a corresponding eigenvalue in the Timoshenko beam model. The authors call all matching eigenvalues beam-type eigenvalues. The authors show that the Timoshenko beam model compare well to the two-dimensional model for long and short beams. The results of the article are verified and extra results are also calculated for the rest of this chapter. In this section, the aricle \cite{LVV09} is extended to verify the validity of the two-dimensional elastic model. The two-dimensional elastic model is compared to a more realistic three-dimensional model. The two dimensional model serves as a intermediate step between the Timoshenko beam model and the three-dimensional model. The same approach of \cite{LVV09} is used to compare the two models. The result show that the two-dimensional model compare very well to the three-dimensional model, especially for beam problems. The last section takes the idea of \cite{LVV09} and extends it to the Reissner-Mindlin plate model. The Reissner-Mindlin plate model is compared to a more realistic three-dimensional plate model.\\

*******************************************************************************
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
